---
title: End to End Covid-19 Analysis with R - Import Data (1)
date: 2020-03-09
categories:
  - Scraping Content
tags:
  - Test
  - Test2

type:  "post"
w3codecolor: false
draft: false
---

<img src="https://www.cradletograver.com/auto-posts/images/EndtoEndCovid-19AnalysiswithR-ImportData(1).webm.jpg">
#CradleToGraveR now a Discord! Come say hello: https://discord.gg/f2uDBvA
THIS VIDEO HAS BEEN UPDATED - CLICK THIS ONE INSTEAD: https://youtu.be/cdFIlaKKbkk

First part, importing Covid-19 (coronavirus) data into R. Note that I changed all of the "less than" symbols to "equal" symbols due to YouTube policy not having angled brackets.

<U+0001F447>SUBSCRIBE & HIT THE <U+0001F44D> BUTTON <U+0001F447>
R Channel: http://bit.ly/38yfFP9
How I Create Videos: http://bit.ly/sub_to_chan

<U+2794> TubeBuddy: http://bit.ly/t_buddy
<U+2794> Blue Yeti Mic: https://amzn.to/2IheZTG
<U+2794> 2 Months SkillShare Free <U+2794>  https://www.skillshare.com/r/profile/Mark-Gingrass/2388101

---
title: "Covid Cases in R"
output: html_notebook
---
# Covid Data Import

This is where we get the data: https://www.ecdc.europa.eu/en/geographical-distribution-2019-ncov-cases

```{r eval=FALSE}
library(httr)
library(readxl)

url1 = "https://www.ecdc.europa.eu/sites/default/files/documents/COVID-19-geographic-disbtribution-worldwide-2020-03-08.xls"

GET(url1, write_disk(tf = tempfile(fileext = ".xls")))

df = read_excel((tf))
```

# Covid Data Clean Up

This is cleaning up of the data.

```{r eval=FALSE}
sum(df$NewDeaths)
```

Do you have more to add? Let me know how you liked the video or if I need anything corrected in the comments below.
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
TECH GEAR I USE DAILY
<U+2794> MacBook Pro: https://amzn.to/2XxeBsG
<U+2794> Blue Yeti Mic: https://amzn.to/2IheZTG
<U+2794> Swissgear Backpack: https://youtu.be/VTTnRMyFkB8
<U+2794> Canon EOS 90D Camera: https://amzn.to/2u0o52K
<U+2794> Apple Magic Trackpad 2: https://amzn.to/31XDugG
<U+2794> mTuber for Title Effects : https://motionvfx.sjv.io/3M3KM
<U+2794> mArrows for animated arrows: https://motionvfx.sjv.io/9B3oe
<U+2794> Microphone - https://amzn.to/2LYfJkr
<U+2794> Backpack - https://amzn.to/2Ep4uez
<U+2794> Green Screen - https://amzn.to/2JVzMgP
<U+2794> Tripod Neewer: https://amzn.to/2uF275X
<U+2794> Tripod (cheap) - https://amzn.to/2Eo2wv4

HOMEPAGE - https://www.markgingrass.com/
REVIEWS/BLOG - https://www.markgingrass.com/blogs/re...

OTHER COURSES I CURRENTLY TEACH
<U+2794> C++ Course: http://bit.ly/cpp_course
<U+2794> Supply Chain Management:  http://bit.ly/scm_course

Let's chat
https://twitter.com/MarkGingrass



c:/ytdl//CradleToGraveR/Practical R for Business/05 - End to End Covid-19 Analysis with R - Import Data (1)/End to End Covid-19 Analysis with R - Import Data (1).webm.en.txt
